Solent region: Test Maps

### 2021-07-30 Solent_Mapping_v2.Rmd
Added section attempting to map change in domestic gas consumption from 2010 to 2019 but getting a momory error

## Mapping Transport

#### Freight
```{r Loading the  Freight Transport consumption data for the Local Autority}
inFile <-paste0(dataFolder, "energy/Local Authority level Transport data.csv")
la_Transport <- readr::read_csv(inFile)
summary(la_Transport)
head(la_Transport)
```

@@

```{r Loading in the 2019 Local Authority Fuel Poverty Data}
inFile<-paste0(dataFolder, "Fuel Poverty/2019 LA_Fuel_Poverty.csv")
la_fuelpov_2019<-readr::read_csv(inFile)
head(la_fuelpov_2019)
```
```{r Mapping Local Authority Fuel Poverty 2019}
la_fuelpov_2019$lad18cd <- la_fuelpov_2019$`Area Codes` # Creating a variable with the local authority code in the same name 
la_merged_Fuelpov2019 <- merge(la_sf_data, la_fuelpov_2019)# Merge the local Authority boundaries and the Fuel Poverty data
la_merged_Fuelpov2019$pcFP <- as.numeric(la_merged_Fuelpov2019$`Proportion of households fuel poor (%)`) # convert to numeric from char - why does it load as char??
ggplot2::ggplot(la_merged_Fuelpov2019) +
  geom_sf(aes(fill = pcFP)) +
  scale_fill_gradient(name = "Proportion of households fuel poor (%)", low="green",high="red")
```

### Difference in proportion Fuel Poverty 2012 to 2019
```{r Creating the idfference in proportion variable}
#Green indicates a smaller increase in fuel poverty from 2012 to 2019
#Red indicates an increase in fuel poverty from 2012 to 2019
fp_LA_2012_df <- readr::read_csv(paste0(dataFolder, "/Fuel Poverty/2012 LA_Fuel_Poverty.csv"))
fp_LA_2019_df <- readr::read_csv(paste0(dataFolder, "/Fuel Poverty/2019 LA_Fuel_Poverty.csv"))
merged_df <- merge(fp_LA_2012_df, fp_LA_2019_df, by = "Area Code", all = TRUE)
names(merged_df)
merged_df$pc_diff <-  as.numeric(merged_df$`Proportion of households fuel poor (%)`) - merged_df$`Proportion of households fuel poor (%) 2012`
```
```{r Mapping the iddference in fuel poverty from 2012 to 2019}
merged_df$lad18cd <- la_fuelpov_2019$`Area Code` # Creating a variable with the local authority code in the same name 
la_merged_Fuelpov20192012dif <- merge(la_sf_data,merged_df)# Merge the local Authority boundaries and the Fuel Poverty data
la_merged_Fuelpov20192012dif$pcFP <- as.numeric(la_merged_Fuelpov20192012dif$`Proportion of households fuel poor (%)`) # convert to numeric from char - why does it load as char??
ggplot2::ggplot(la_merged_Fuelpov20192012dif) +
  geom_sf(aes(fill = pc_diff)) +
  scale_fill_gradient(name = " Difference in proportion of households fuel poor (%)", low="green",high="red")
```

###Difference in proportion between 2012-2019

# Mapping the Middle Layer Super Output Areas (MSOA)

### Mapping the Electricity Consumption

@@

```{r Mapping the electrcity consumption of the MSOAs}
msoa_elecData$MSOA11CD <- msoa_elecData$ 'Middle Layer Super Output Area (MSOA) Code' #Creating a variable with the LA code and the name as in the sf_data
msoa_merged_sf <-merge(msoa_sf_data, msoa_elecData)
ggplot2::ggplot(msoa_merged_sf) + 
  geom_sf(aes(fill = `Mean consumption (kWh per meter)`)) +
  scale_fill_continuous(name = "Electricity: Mean kWh per meter", low = "green", high = "red") +
  labs(caption = "Solent (all MSOAs)")
#mapping it
```

### Mapping the Gas
```{r Loading in the MSOA gas consumption data}
# gas consumption data at MSOA level (pre downloaded)
inFile <-paste0(dataFolder, "energy/MSOA_GAS_2019.csv")
msoa_gasData <- readr::read_csv(inFile)
head(msoa_gasData)
```
```{r Mapping the gas consumption of the MSOAs}
msoa_gasData$MSOA11CD <- msoa_gasData$ 'Middle Layer Super Output Area (MSOA) Code' 
msoa_merged_sf_domgas <-merge(msoa_sf_data, msoa_gasData)
ggplot2::ggplot(msoa_merged_sf_domgas) + 
  geom_sf(aes(fill = `Mean consumption (kWh per meter)`)) +
  scale_fill_continuous(name = "Gas: Mean kWh per meter", low = "green", high = "red") +
  labs(caption = "Solent (all MSOAs)")
#mapping it
```
> Does this match to non-gas areas??

@@

```{r Mapping the electrcity consumption of the MSOAs Industrial Sector}
msoa_elecDatanondom$MSOA11CD <- msoa_elecDatanondom$ 'Middle Layer Super Output Area (MSOA) Code' 
msoa_merged_sf_nondom <-merge(msoa_sf_data, msoa_elecDatanondom)
ggplot2::ggplot(msoa_merged_sf_nondom) + 
  geom_sf(aes(fill = `Mean consumption (kWh per meter)`)) +
  scale_fill_continuous(name = "Electricity: Mean kWh per meter", low = "green", high = "red") +
  labs(caption = "Solent (all MSOAs)")
#mapping it
```
### Mapping Gas

>>>>

## Mapping Transport
#### Freight
```{r Loading the  Freight Transport consumption data for the Local Autority}
inFile <-paste0(dataFolder, "energy/Local Authority level Transport data.csv")
la_Transport <- readr::read_csv(inFile)
summary(la_Transport)
head(la_Transport)
```

@@

```{r Loading in the 2019 Local Authority Fuel Poverty Data}
inFile<-paste0(dataFolder, "Fuel Poverty/2019 LA_Fuel_Poverty.csv")
la_fuelpov_2019<-readr::read_csv(inFile)
head(la_fuelpov_2019)
```
```{r Mapping Local Authority Fuel Poverty 2019}
la_fuelpov_2019$lad18cd <- la_fuelpov_2019$`Area Code` # Creating a variable with the local authority code in the same name 
la_merged_Fuelpov2019 <- merge(la_sf_data, la_fuelpov_2019)# Merge the local Authority boundaries and the Fuel Poverty data
la_merged_Fuelpov2019$pcFP <- as.numeric(la_merged_Fuelpov2019$`Proportion of households fuel poor (%)`) # convert to numeric from char - why does it load as char??
ggplot2::ggplot(la_merged_Fuelpov2019) +
  geom_sf(aes(fill = pcFP)) +
  scale_fill_gradient(name = "Proportion of households fuel poor (%)", low="green",high="red")
```
### Difference in proportion Fuel Poverty 2012 to 2019
```{r Creating the idfference in proportion variable}
#Green indicates a smaller increase in fuel poverty from 2012 to 2019
#Red indicates an increase in fuel poverty from 2012 to 2019
fp_LA_2012_df <- readr::read_csv(paste0(dataFolder, "/Fuel Poverty/2012 LA_Fuel_Poverty.csv"))
fp_LA_2019_df <- readr::read_csv(paste0(dataFolder, "/Fuel Poverty/2019 LA_Fuel_Poverty.csv"))
merged_df <- merge(fp_LA_2012_df, fp_LA_2019_df, by = "Area Code", all = TRUE)
names(merged_df)
merged_df$pc_diff <-  as.numeric(merged_df$`Proportion of households fuel poor (%)`) - merged_df$`Proportion of households fuel poor (%) 2012`
```
```{r Mapping the iddference in fuel poverty from 2012 to 2019}
merged_df$lad18cd <- la_fuelpov_2019$`Area Code` # Creating a variable with the local authority code in the same name 
la_merged_Fuelpov20192012dif <- merge(la_sf_data,merged_df)# Merge the local Authority boundaries and the Fuel Poverty data
la_merged_Fuelpov20192012dif$pcFP <- as.numeric(la_merged_Fuelpov20192012dif$`Proportion of households fuel poor (%)`) # convert to numeric from char - why does it load as char??
ggplot2::ggplot(la_merged_Fuelpov20192012dif) +
  geom_sf(aes(fill = pc_diff)) +
  scale_fill_gradient(name = " Difference in proportion of households fuel poor (%)", low="green",high="red")
```
# Mapping the Middle Layer Super Output Areas (MSOA)
## Mapping Domestic
### Mapping the Electricity Consumption

@@

```{r Mapping the electrcity consumption of the MSOAs}
msoa_elecData$MSOA11CD <- msoa_elecData$ 'Middle Layer Super Output Area (MSOA) Code' #Creating a variable with the LA code and the name as in the sf_data
msoa_merged_sf <-merge(msoa_sf_data, msoa_elecData)
ggplot2::ggplot(msoa_merged_sf) + 
  geom_sf(aes(fill = `Mean consumption (kWh per meter)`)) +
  scale_fill_continuous(name = "Electricity: Mean kWh per meter", low = "green", high = "red") +
  labs(caption = "Solent (all MSOAs)")
#mapping it
```
### Mapping the Gas
```{r Loading in the MSOA gas consumption data}
# gas consumption data at MSOA level (pre downloaded)
inFile <-paste0(dataFolder, "energy/MSOA_GAS_2019.csv")
msoa_gasData <- readr::read_csv(inFile)
head(msoa_gasData)
```
```{r Mapping the gas consumption of the MSOAs}
msoa_gasData$MSOA11CD <- msoa_gasData$ 'Middle Layer Super Output Area (MSOA) Code' 
msoa_merged_sf_domgas <-merge(msoa_sf_data, msoa_gasData)
ggplot2::ggplot(msoa_merged_sf_domgas) + 
  geom_sf(aes(fill = `Mean consumption (kWh per meter)`)) +
  scale_fill_continuous(name = "Gas: Mean kWh per meter", low = "green", high = "red") +
  labs(caption = "Solent (all MSOAs)")
#mapping it
```
> Does this match to non-gas areas??

####Mapping the change in gas consumption from 2010 to 2019
```{r Creating the dfference in consumption variable}
#Green indicates a decrease in gas consumption from 2010 to 2019
#Red indicates an increase in gas consumption from 2010 to 2019
domgas_MSOA_2010 <- readr::read_csv(paste0(dataFolder, "/energy/MSOA_GAS_2010.csv"))
domgas_MSOA_2019 <- readr::read_csv(paste0(dataFolder, "/energy/MSOA_GAS_2019.csv"))
domgas_MSOA_2010$domgas2010 <- domgas_MSOA_2010$`Mean consumption (kWh per meter)`
domgas_MSOA_2019$domgas2019 <- domgas_MSOA_2019$`Mean consumption (kWh per meter)`
merged_domgas <- merge(domgas_MSOA_2010, domgas_MSOA_2019, by = "Middle Layer Super Output Area (MSOA) Code", all = TRUE)
names(merged_domgas)
merged_domgas$mc_diff <-  as.numeric(merged_domgas$domgas2019) - merged_domgas$domgas2010
summary(merged_domgas)
```

```{r Mapping the change in dom mean gas comsumption}
merged_domgas$MSOA11CD <- merged_domgas$"MSOA Code" #creating a variable with the LSOA code in the same name as in sf_data
msoa_domgas20102019 <- merge(msoa_sf_data, merged_domgas) #merging these
ggplot2::ggplot(msoa_domgas20102019) +
  geom_sf(aes(fill=mc_diff))+ 
  scale_fill_continuous(name="Change in Gas: Mean kWh per meter", low="green",high="red")+
  labs(caption ="Solent (all MSOAs)")
##Error saying "Could not reallocate memory"
```

@@

```{r Mapping the electrcity consumption of the MSOAs Industrial Sector}
msoa_elecDatanondom$MSOA11CD <- msoa_elecDatanondom$ 'Middle Layer Super Output Area (MSOA) Code' 
msoa_merged_sf_nondom <-merge(msoa_sf_data, msoa_elecDatanondom)
ggplot2::ggplot(msoa_merged_sf_nondom) + 
  geom_sf(aes(fill = `Mean consumption (kWh per meter)`)) +
  scale_fill_continuous(name = "Electricity: Mean kWh per meter", low = "green", high = "red") +
  labs(caption = "Solent (all MSOAs)")
#mapping it
```
####
